### 2022-07-26 src/text/4-project.tex
Add release cycle description

\subsection{Release Cycle, Versioning, and Long-term Support}
With the first long term support (LTS) releases v1.0, the \gammapy project
enters a new development phase.
\todo{To be written...summarise and reference PIG 24}

>>>>

\subsection{Release Cycle, Versioning, and Long-term Support}
With the first long term support (LTS) release v1.0, the \gammapy project
enters a new development phase. The development will change from
quick feature driven development to more stable maintenance
and user support driven developement. After v1.0 we foresee
a developement cycle with major, minor and bugfix releases.
We basically followg the development cycle of the Astropy
project. Thus we expect a major LTS release approximately
every two years, minor releases are planned every 6~months,
while bug-fix releases will happen as needed. While
bug-fix releases will not introduce API breaking changes,
we will work with a deprecation system for minor releases.
API breaking changes will be announced to user by runtime
warnings first and then implemented in the subsequent
minor release. This approach we consider a fair
compromise between the interests of users in a stable
package and the interest of developers to improve
and develop \gammapy in future. The developemnt cycle is described
in more detail in PIG 24 \todo{reference}.
